---
title: Pregancy project participant information summary
author: Xiaotao Shen
date: '2019-10-30'
slug: pregancy-project-participant-information-summary
categories:
  - literature
tags:
  - Blog
image:
  caption: ''
  focal_point: ''
output:
  blogdown::html_page:
    toc: true
    number_sections: true
---

# Maternal DOB

Maternal date of birth.

# Age

Mother age.

# Marital Status

Mothers' marriage status

```{r echo=FALSE, results="asis"}
library(knitr)
kable(
  data.frame(
    Lable = c("Married, FOB involved",
              "Unknown, FOB involved",
              "Single, FOB involved",
              "Unknown",
              "NA",
              "Unmarried, FOB involved",
              "Unmarried, FOB involved, but not living together",
              "Unmarried, FOB not involved",
              "unknown, FOB involved but living separately",
              "Single"
              ),
               
    Meaning = c("Married, FOB involved",
              "Unknown, FOB involved",
              "Single, FOB involved",
              "Unknown",
              "NA",
              "Unmarried, FOB involved",
              "Unmarried, FOB involved, but not living together",
              "Unmarried, FOB not involved",
              "unknown, FOB involved but living separately",
              "Single"
              )
  )
)
```


**Note**:
  
I don't know what the meaning of "FOB involved".

# Ethinic Group

The ethnicity of mothers.

```{r echo=FALSE, results="asis"}
library(knitr)
kable(
  data.frame(
    Lable = c("Afr Am",
              "4 (Asian)",
              "1",
              "2",
              "3",
              "4",
              "5"
              ),
               
    Meaning = c("Black",
                "Asian",
                "White",
                "Black",
                "Latina",
                "Pacific Islander",
                "Asian"
              )
  )
)
```

# Employed

The mothers' work status.

# Housing

House status.

# Parity

Gravidity is defined as the number of times that a woman has been pregnant. 

**Note**:

[8] "G4P1021"     "G3P1011"     NA            "G5P2"        "G5P0"        "G10P3154"    "G3P2002"    
[15] "G4P2012"     "G4P0303"     "G6P5005"     "G14P4-1-8-4" "G4P3003"     "G7P4115"     "G9P4044"    
[22] "G5P2022"     "G5P2113"     "G5P0040"     "G8P5025"  

I don not understand what that means.


# PMH

I don't understand what this means, but it may be mothers's diesease.

# PSH

I don't understand what this means.

# OB hx

I donn't understand what this means.

# Genetic testing

Genetic testing for mothers.

# 








